---
title: "Tossing a coin: Preferences for random allocation in triage decisions"
output: html_notebook
---

# Versions

R version 4.4.1 (2024-06-14)
Platform: aarch64-apple-darwin20
Running under: macOS Sonoma 14.6

Matrix products: default
BLAS:   /System/Library/Frameworks/Accelerate.framework/Versions/A/Frameworks/vecLib.framework/Versions/A/libBLAS.dylib 
LAPACK: /Library/Frameworks/R.framework/Versions/4.4-arm64/Resources/lib/libRlapack.dylib;  LAPACK version 3.12.0

locale:
[1] en_US.UTF-8/en_US.UTF-8/en_US.UTF-8/C/en_US.UTF-8/en_US.UTF-8

time zone: Europe/Berlin
tzcode source: internal

attached base packages:
[1] stats     graphics  grDevices utils     datasets  methods   base     

other attached packages:
 [1] janitor_2.2.0       lubridate_1.9.3     forcats_1.0.0       stringr_1.5.1       dplyr_1.1.4         purrr_1.0.2         readr_2.1.5        
 [8] tidyr_1.3.1         tibble_3.2.1        ggplot2_3.5.1       tidyverse_2.0.0     ggthemes_5.1.0      bife_0.7.2          survival_3.6-4     
[15] margins_0.3.28      ordinal_2023.12-4.1 magrittr_2.0.3      lmerTest_3.1-3      lme4_1.1-35.5       Matrix_1.7-0       

loaded via a namespace (and not attached):
 [1] gtable_0.3.6        prediction_0.3.18   xfun_0.48           bslib_0.8.0         lattice_0.22-6      tzdb_0.4.0          numDeriv_2016.8-1.1
 [8] vctrs_0.6.5         tools_4.4.1         generics_0.1.3      fansi_1.0.6         ucminf_1.2.2        pkgconfig_2.0.3     data.table_1.16.2  
[15] lifecycle_1.0.4     compiler_4.4.1      farver_2.1.2        munsell_0.5.1       snakecase_0.11.1    sass_0.4.9          htmltools_0.5.8.1  
[22] yaml_2.3.10         Formula_1.2-5       pillar_1.9.0        nloptr_2.1.1        jquerylib_0.1.4     MASS_7.3-60.2       cachem_1.1.0       
[29] boot_1.3-30         nlme_3.1-164        tidyselect_1.2.1    digest_0.6.37       stringi_1.8.4       labeling_0.4.3      splines_4.4.1      
[36] fastmap_1.2.0       grid_4.4.1          colorspace_2.1-1    cli_3.6.3           utf8_1.2.4          withr_3.0.2         scales_1.3.0       
[43] timechange_0.3.0    rmarkdown_2.28      hms_1.1.3           evaluate_1.0.1      knitr_1.48          rlang_1.1.4         Rcpp_1.0.13        
[50] glue_1.8.0          jsonlite_1.8.9      rstudioapi_0.17.1   minqa_1.2.8         R6_2.5.1

# Packages

```{r}
#> install.packages("lme4")
#> install.packages("lmerTest")
#> install.packages("magrittr")
#> install.packages("ordinal")
#> install.packages("margins")
#> install.packages("survival")
#> install.packages("bife")
#> install.packages("janitor")
#> install.packages("ggthemes")
#> install.packages("tidyverse")

library(lme4)
library(lmerTest)
library(magrittr)
library(ordinal)
library(margins)
library(survival)
library(bife)
library(janitor)
library(tidyverse)
library(ggthemes)
```

# Data preparation

```{r}
data <- 
  readRDS(file = "data/df_triage_final.rds") %>% 
  filter(bot_all & time >= 5)
```

# Figures

## Figure 1

```{r}
data %>% 
  select("id", 
         "vig_set", 
         "vig_choice"
         ) %>% 
  group_by(id, vig_set) %>%
  mutate(random = if_else(condition = any(vig_choice == 3),
                          true = 1,
                          false = 0
                          )
         ) %>% 
  ungroup() %>% 
  select(-"vig_choice") %>%
  unique() %>% 
  group_by(id) %>%
  summarise(sum_random = sum(random)) %>% 
  ungroup() %>% 
  count(sum_random) %>% 
  mutate(prop = n / sum(n)) %>%
  ggplot(mapping = aes(x = sum_random,
                       y = prop
                       )
         ) +
  geom_bar(stat = "identity") +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks = seq(0, 5, by = 1)) +
  geom_text(mapping = aes(label = scales::percent(prop)),
            vjust = -0.5,
            family = "serif"
            ) +
  labs(x = "Number of allocations by random lottery",
       y = "Proportion of participants"
       ) +
  theme_clean() +
  theme(text = element_text(size = 12,
                            family = "serif"
                            ),
        plot.background = element_blank()
        )
```

## Figure 2

```{r}
data %>% 
  select("id", 
         contains("vig_")
         ) %>% 
  filter(vig_choice != 3) %>% 
  lmer(formula = vig_choice ~ vig_weight + 
                              vig_age + 
                              vig_chance_of_survival_with_ventilation +
                              vig_ventilation_status + 
                              vig_children +
                              vig_disability + 
                              vig_volunteer_work + 
                              vig_vaccination_status + 
                              (1|id),
       data = .
       ) %>% 
  confint(.,
          method = "Wald"
          ) %>%
  as_tibble(.,
            rownames = "eff"
            ) %>% 
  clean_names() %>% 
  mutate(effect = NA) %>%
  add_case(eff = c("20% chance of survival (Ref.)", "25 years old (Ref.)"),
           effect = 0,
           x97_5_percent = NA,
           x2_5_percent = NA
           ) %>% 
  transmute(x2_5_percent,
            x97_5_percent,
            effect = if_else(condition = is.na(effect),
                             true = .$x2_5_percent + (.$x97_5_percent - .$x2_5_percent) / 2,
                             false = effect
                             ),
            attr = str_extract(eff, 
                            "[A-Z0-9].*"
                            ),
            attr = factor(attr,
                          levels = c("20% chance of survival (Ref.)",
                                     "50% chance of survival",
                                     "80% chance of survival",
                                     "25 years old (Ref.)",
                                     "50 years old",
                                     "75 years old",
                                     "Has a disability",
                                     "Overweight",
                                     "Is already ventilated",
                                     "Is vaccinated",
                                     "Does volunteer work",
                                     "Has children"
                                     ),
                          labels = c("20% chance of survival (Ref.)",
                                     "50% chance of survival",
                                     "80% chance of survival",
                                     "25 years old (Ref.)",
                                     "50 years old",
                                     "75 years old",
                                     "Has a disability",
                                     "Is overweight",
                                     "Is already ventilated",
                                     "Is vaccinated",
                                     "Does volunteer work",
                                     "Has children"
                                     )
                          ),
            attr = fct_rev(attr)
            ) %>%
  filter(!is.na(attr)) %>%
  ggplot(mapping = aes(x = attr, 
                       y = effect
                       )
         ) +
   geom_hline(yintercept = 0,
              linetype = "dashed"
              ) +
  geom_errorbar(mapping = aes(ymin = x2_5_percent,
                              ymax = x97_5_percent
                              ),
                width = 0.25
                ) +
  geom_point() +
  labs(x = "",
       y = "AMCE",
       color = "Condition",
       shape = "Condition"
       ) +
  coord_flip() +
  theme_clean() +
  theme(text = element_text(size = 12,
                            family = "serif"
                            ),
        legend.title = element_text(size = 9,
                                    family = "serif"
                                    ),
        legend.text = element_text(size = 9,
                                   family = "serif"
                                   ),
        plot.background = element_blank()
        )
```

### Regression table

```{r}
data %>% 
  filter(vig_choice != 3) %>% 
  lmer(formula = vig_choice ~ vig_weight + 
                              vig_age + 
                              vig_chance_of_survival_with_ventilation +
                              vig_ventilation_status + 
                              vig_children +
                              vig_disability + 
                              vig_volunteer_work + 
                              vig_vaccination_status + 
                              (1|id),
       data = .
       ) %>% 
  summary()
```

## Figure 3

```{r}
data %>% 
  select("id", 
         contains("vig_")
         ) %>% 
  group_by(id, 
           vig_set
           ) %>% 
  transmute(id,
            vig_set,
            random = if_else(any(vig_choice == 3),
                          true = 1,
                          false = 0
                          ),
         same_survival = if_else(length(unique(vig_chance_of_survival_with_ventilation)) == 1,
                                 true = 1,
                                 false = 0
                                 ),
         same_age = if_else(length(unique(vig_age)) == 1,
                                 true = 1,
                                 false = 0
                                 ),
         same_vaccination = if_else(length(unique(vig_vaccination_status)) == 1,
                                 true = 1,
                                 false = 0
                                 ),
         same_volunteer = if_else(length(unique(vig_volunteer_work)) == 1,
                                 true = 1,
                                 false = 0
                                 ),
         same_disability = if_else(length(unique(vig_disability)) == 1,
                                 true = 1,
                                 false = 0
                                 ),
         same_children = if_else(length(unique(vig_children)) == 1,
                                 true = 1,
                                 false = 0
                                 ),
         same_ventilation = if_else(length(unique(vig_ventilation_status)) == 1,
                                 true = 1,
                                 false = 0
                                 ),
         same_weight = if_else(length(unique(vig_weight)) == 1,
                                 true = 1,
                                 false = 0
                                 )
         ) %>%
    ungroup() %>% 
  distinct() %$%
  clogit(formula = random ~ same_survival + 
                            same_age + 
                            same_disability + 
                            same_weight + 
                            same_ventilation + 
                            same_vaccination + 
                            same_volunteer + 
                            same_children + 
                            strata(id)
         ) %>% 
  confint(., 
          method = "Wald"
          ) %>%
  as_tibble(.,
            rownames = "variable"
            ) %>% 
  clean_names() %>% 
  mutate(coef = x2_5_percent + (x97_5_percent - x2_5_percent) / 2,
         variable = factor(variable,
                           levels = c("same_survival",
                                      "same_age",
                                      "same_disability",
                                      "same_weight",
                                      "same_ventilation",
                                      "same_vaccination",
                                      "same_volunteer",
                                      "same_children"),
                           labels = c("Chance of survival is equal",
                                      "Age is equal",
                                      "Disability is equal",
                                      "Overweight is equal",
                                      "Ventilation status is equal",
                                      "Vaccination status is equal",
                                      "Volunteer work is equal",
                                      "Children is equal")
                           ),
         variable = fct_rev(variable),
         coef = exp(coef),
         x2_5_percent = exp(x2_5_percent),
         x97_5_percent = exp(x97_5_percent)
         ) %>% 
  ggplot(mapping = aes(x = coef,
                       y = variable
                       )
         ) +
  geom_vline(xintercept = 1,
             linetype = "dashed"
             ) +
  geom_point() +
  geom_errorbar(mapping = aes(xmin = x2_5_percent,
                              xmax = x97_5_percent),
                width = 0.25
                ) +
  labs(x = "OR",
       y = "",
       ) +
  scale_x_continuous(breaks = seq(from = 1, 
                                  to = 2.5, 
                                  by = 0.5)) +
  theme_clean() +
  theme(text = element_text(size = 12,
                            family = "serif"
                            ),
        plot.background = element_blank()
        )
```

### Regression table

```{r}
data %>% 
  select("id", 
         contains("vig_")
         ) %>% 
  group_by(id, 
           vig_set
           ) %>% 
  transmute(id,
            vig_set,
            random = if_else(any(vig_choice == 3),
                          true = 1,
                          false = 0
                          ),
            same_survival = if_else(length(unique(vig_chance_of_survival_with_ventilation)) == 1,
                                    true = 1,
                                    false = 0
                                    ),
            same_age = if_else(length(unique(vig_age)) == 1,
                               true = 1,
                               false = 0
                               ),
            same_vaccination = if_else(length(unique(vig_vaccination_status)) == 1,
                                       true = 1,
                                       false = 0
                                       ),
            same_volunteer = if_else(length(unique(vig_volunteer_work)) == 1,
                                     true = 1,
                                     false = 0
                                     ),
            same_disability = if_else(length(unique(vig_disability)) == 1,
                                      true = 1,
                                      false = 0
                                      ),
            same_children = if_else(length(unique(vig_children)) == 1,
                                    true = 1,
                                    false = 0
                                    ),
            same_ventilation = if_else(length(unique(vig_ventilation_status)) == 1,
                                       true = 1,
                                       false = 0
                                       ),
            same_weight = if_else(length(unique(vig_weight)) == 1,
                                  true = 1,
                                  false = 0
                                  )
            ) %>%
  ungroup() %>%
  distinct() %$%
  clogit(formula = random ~ same_survival + 
                            same_age + 
                            same_disability + 
                            same_weight + 
                            same_ventilation + 
                            same_vaccination + 
                            same_volunteer + 
                            same_children + 
                            strata(id)
         ) %>% 
  summary()
```

## Figure 4

```{r}
data %>% 
  select("id", 
         contains("vig_"), 
         "fairness_random"
         ) %>% 
  group_by(id, 
           vig_set
           ) %>% 
  transmute(id,
            vig_set,
            random = if_else(any(vig_choice == 3),
                             true = 1,
                             false = 0
                             ),
            fairness_random,
            same_survival = if_else(length(unique(vig_chance_of_survival_with_ventilation)) == 1,
                                    true = 1,
                                    false = 0
                                    ),
            same_age = if_else(length(unique(vig_age)) == 1,
                                      true = 1,
                                      false = 0
                               ),
            same_vaccination = if_else(length(unique(vig_vaccination_status)) == 1,
                                       true = 1,
                                       false = 0
                                       ),
            same_volunteer = if_else(length(unique(vig_volunteer_work)) == 1,
                                     true = 1,
                                     false = 0
                                     ),
            same_disability = if_else(length(unique(vig_disability)) == 1,
                                      true = 1,
                                      false = 0
                                      ),
            same_children = if_else(length(unique(vig_children)) == 1,
                                    true = 1,
                                    false = 0
                                    ),
            same_ventilation = if_else(length(unique(vig_ventilation_status)) == 1,
                                       true = 1,
                                       false = 0
                                       ),
            same_weight = if_else(length(unique(vig_weight)) == 1,
                                  true = 1,
                                  false = 0
                                  )
            ) %>%
  ungroup() %>% 
  distinct() %>% 
  filter(as.logical(random)) %$%
  lmer(fairness_random ~ same_survival + 
                         same_age + 
                         same_vaccination + 
                         same_volunteer + 
                         same_disability + 
                         same_children + 
                         same_ventilation + 
                         same_weight + 
                         (1|id)
       ) %>%
  confint(., 
          method = "Wald"
          ) %>%
  as_tibble(.,
            rownames = "variable"
            ) %>% 
  clean_names() %>% 
  mutate(coef = x2_5_percent + (x97_5_percent - x2_5_percent) / 2,
         variable = factor(variable,
                           levels = c("same_survival",
                                      "same_age",
                                      "same_disability",
                                      "same_weight",
                                      "same_ventilation",
                                      "same_vaccination",
                                      "same_volunteer",
                                      "same_children"),
                           labels = c("Chance of survival is equal",
                                      "Age is equal",
                                      "Disability is equal",
                                      "Overweight is equal",
                                      "Ventilation status is equal",
                                      "Vaccination status is equal",
                                      "Volunteer work is equal",
                                      "Children is equal")
                           ),
         variable = fct_rev(variable)
         ) %>%
  filter(!is.na(variable)) %>% 
  ggplot(mapping = aes(x = coef,
                       y = variable
                       )
         ) +
  geom_vline(xintercept = 0,
             linetype = "dashed"
             ) +
  geom_point() +
  geom_errorbar(mapping = aes(xmin = x2_5_percent,
                              xmax = x97_5_percent
                              ),
                width = 0.25
                ) +
  labs(x = "Coefficients (OLS)",
       y = "",
       ) +
  theme_clean() +
  theme(text = element_text(size = 12,
                            family = "serif"
                            ),
        plot.background = element_blank()
        )
```

### Regression table

```{r}
data %>% 
  select("id", 
         contains("vig_"), 
         "fairness_random"
         ) %>% 
  group_by(id, 
           vig_set
           ) %>% 
  transmute(id,
            vig_set,
            random = if_else(any(vig_choice == 3),
                             true = 1,
                             false = 0
                             ),
            fairness_random,
            same_survival = if_else(length(unique(vig_chance_of_survival_with_ventilation)) == 1,
                                    true = 1,
                                    false = 0
                                    ),
            same_age = if_else(length(unique(vig_age)) == 1,
                                      true = 1,
                                      false = 0
                               ),
            same_vaccination = if_else(length(unique(vig_vaccination_status)) == 1,
                                       true = 1,
                                       false = 0
                                       ),
            same_volunteer = if_else(length(unique(vig_volunteer_work)) == 1,
                                     true = 1,
                                     false = 0
                                     ),
            same_disability = if_else(length(unique(vig_disability)) == 1,
                                      true = 1,
                                      false = 0
                                      ),
            same_children = if_else(length(unique(vig_children)) == 1,
                                    true = 1,
                                    false = 0
                                    ),
            same_ventilation = if_else(length(unique(vig_ventilation_status)) == 1,
                                       true = 1,
                                       false = 0
                                       ),
            same_weight = if_else(length(unique(vig_weight)) == 1,
                                  true = 1,
                                  false = 0
                                  )
            ) %>%
  ungroup() %>% 
  distinct() %>% 
  filter(as.logical(random)) %$%
  lmer(fairness_random ~ same_survival + 
                         same_age + 
                         same_vaccination + 
                         same_volunteer + 
                         same_disability + 
                         same_children + 
                         same_ventilation + 
                         same_weight + 
                         (1|id)
       ) %>% 
  summary()
```

## Figure A4

```{r}
data %>% 
  dplyr::select("id", contains("vig_"), "fairness_random") %>% 
  group_by(id, 
           vig_set
           ) %>% 
  transmute(id,
            vig_set,
            random = if_else(any(vig_choice == 3),
                             true = 1,
                             false = 0
                             ),
            fairness_random = factor(fairness_random,
                                     levels = 1:6,
                                     ordered = TRUE),
            same_survival = if_else(length(unique(vig_chance_of_survival_with_ventilation)) == 1,
                                    true = 1,
                                    false = 0
                                    ),
            same_age = if_else(length(unique(vig_age)) == 1,
                                      true = 1,
                                      false = 0
                               ),
            same_vaccination = if_else(length(unique(vig_vaccination_status)) == 1,
                                       true = 1,
                                       false = 0
                                       ),
            same_volunteer = if_else(length(unique(vig_volunteer_work)) == 1,
                                     true = 1,
                                     false = 0
                                     ),
            same_disability = if_else(length(unique(vig_disability)) == 1,
                                      true = 1,
                                      false = 0
                                      ),
            same_children = if_else(length(unique(vig_children)) == 1,
                                    true = 1,
                                    false = 0
                                    ),
            same_ventilation = if_else(length(unique(vig_ventilation_status)) == 1,
                                       true = 1,
                                       false = 0
                                       ),
            same_weight = if_else(length(unique(vig_weight)) == 1,
                                  true = 1,
                                  false = 0
                                  )
            ) %>%
  ungroup() %>% 
  distinct() %>% 
  filter(as.logical(random)) %$%
  clmm(fairness_random ~ same_survival + 
                         same_age + 
                         same_vaccination + 
                         same_volunteer + 
                         same_disability + 
                         same_children + 
                         same_ventilation + 
                         same_weight + 
                         (1|id),
                         data = .,
                         link = "logit"
       ) %>%
  confint(., 
          method = "Wald"
          ) -> ci_ordinal


data_ordinal <- 
  ci_ordinal %>%
  as_tibble(.,
            rownames = "variable") %>% 
  clean_names() %>% 
  mutate(coef = x2_5_percent + (x97_5_percent - x2_5_percent) / 2,
         variable = factor(variable,
                           levels = c("same_survival",
                                      "same_age",
                                      "same_disability",
                                      "same_weight",
                                      "same_ventilation",
                                      "same_vaccination",
                                      "same_volunteer",
                                      "same_children"),
                           labels = c("Chance of survival is equal",
                                      "Age is equal",
                                      "Disability is equal",
                                      "Overweight is equal",
                                      "Ventilation status is equal",
                                      "Vaccination status is equal",
                                      "Volunteer work is equal",
                                      "Children is equal")
                           ),
         variable = fct_rev(variable),
         model = "CLMM"
         ) %>% 
  filter(!is.na(variable))

data_ols <-
  data %>% 
  select("id", 
         contains("vig_"), 
         "fairness_random"
         ) %>% 
  group_by(id, 
           vig_set
           ) %>% 
  transmute(id,
            vig_set,
            random = if_else(any(vig_choice == 3),
                             true = 1,
                             false = 0
                             ),
            fairness_random,
            same_survival = if_else(length(unique(vig_chance_of_survival_with_ventilation)) == 1,
                                    true = 1,
                                    false = 0
                                    ),
            same_age = if_else(length(unique(vig_age)) == 1,
                                      true = 1,
                                      false = 0
                               ),
            same_vaccination = if_else(length(unique(vig_vaccination_status)) == 1,
                                       true = 1,
                                       false = 0
                                       ),
            same_volunteer = if_else(length(unique(vig_volunteer_work)) == 1,
                                     true = 1,
                                     false = 0
                                     ),
            same_disability = if_else(length(unique(vig_disability)) == 1,
                                      true = 1,
                                      false = 0
                                      ),
            same_children = if_else(length(unique(vig_children)) == 1,
                                    true = 1,
                                    false = 0
                                    ),
            same_ventilation = if_else(length(unique(vig_ventilation_status)) == 1,
                                       true = 1,
                                       false = 0
                                       ),
            same_weight = if_else(length(unique(vig_weight)) == 1,
                                  true = 1,
                                  false = 0
                                  )
            ) %>%
  ungroup() %>% 
  distinct() %>% 
  filter(as.logical(random)) %$%
  lmer(fairness_random ~ same_survival + 
                         same_age + 
                         same_vaccination + 
                         same_volunteer + 
                         same_disability + 
                         same_children + 
                         same_ventilation + 
                         same_weight + 
                         (1|id)
       ) %>%
  confint(., 
          method = "Wald"
          ) %>%
  as_tibble(.,
            rownames = "variable"
            ) %>% 
  clean_names() %>% 
  mutate(coef = x2_5_percent + (x97_5_percent - x2_5_percent) / 2,
         variable = factor(variable,
                           levels = c("same_survival",
                                      "same_age",
                                      "same_disability",
                                      "same_weight",
                                      "same_ventilation",
                                      "same_vaccination",
                                      "same_volunteer",
                                      "same_children"),
                           labels = c("Chance of survival is equal",
                                      "Age is equal",
                                      "Disability is equal",
                                      "Overweight is equal",
                                      "Ventilation status is equal",
                                      "Vaccination status is equal",
                                      "Volunteer work is equal",
                                      "Children is equal")
                           ),
         variable = fct_rev(variable),
         model = "OLS (Figure 3 in main text)"
         ) %>%
  filter(!is.na(variable))

bind_rows(data_ordinal, data_ols) %>%
  ggplot(mapping = aes(x = coef,
                       y = variable
                       )
         ) +
  geom_vline(xintercept = 0,
             linetype = "dashed"
             ) +
  geom_point() +
  geom_errorbar(mapping = aes(xmin = x2_5_percent,
                              xmax = x97_5_percent
                              ),
                width = 0.25
                ) +
  labs(x = "Coefficients",
       y = "",
       ) +
  theme_clean() +
  theme(text = element_text(size = 12,
                            family = "serif"
                            ),
        plot.background = element_blank()
        ) +
  facet_grid(cols = vars(model),
             scales = "free_x"
             )
```

### Regression table (CLMM)

```{r}
data %>% 
  dplyr::select("id", contains("vig_"), "fairness_random") %>% 
  group_by(id, vig_set) %>% 
  transmute(id,
            vig_set,
            random = if_else(any(vig_choice == 3),
                          true = 1,
                          false = 0
                          ),
            fairness_random = factor(fairness_random,
                                     levels = 1:6,
                                     ordered = TRUE),
         same_survival = if_else(length(unique(vig_chance_of_survival_with_ventilation)) == 1,
                                 true = 1,
                                 false = 0
                                 ),
         same_age = if_else(length(unique(vig_age)) == 1,
                                 true = 1,
                                 false = 0
                                 ),
         same_vaccination = if_else(length(unique(vig_vaccination_status)) == 1,
                                 true = 1,
                                 false = 0
                                 ),
         same_volunteer = if_else(length(unique(vig_volunteer_work)) == 1,
                                 true = 1,
                                 false = 0
                                 ),
         same_disability = if_else(length(unique(vig_disability)) == 1,
                                 true = 1,
                                 false = 0
                                 ),
         same_children = if_else(length(unique(vig_children)) == 1,
                                 true = 1,
                                 false = 0
                                 ),
         same_ventilation = if_else(length(unique(vig_ventilation_status)) == 1,
                                 true = 1,
                                 false = 0
                                 ),
         same_weight = if_else(length(unique(vig_weight)) == 1,
                                 true = 1,
                                 false = 0
                                 )
         ) %>%
    ungroup() %>% 
  distinct() %>% 
  filter(as.logical(random)) %$%
  clmm(fairness_random ~ same_survival + 
                         same_age + 
                         same_vaccination + 
                         same_volunteer + 
                         same_disability + 
                         same_children + 
                         same_ventilation + 
                         same_weight + 
                         (1|id),
                         data = .,
                         link = "logit"
       ) %>% 
  summary()
```